Adaptive Computation of Sobol' Indices

### 2016-02-16 SobolIndices.tex
Finishing the algorithm for the Sobol Indices with examples and fixing a few typos.
small change
Fixing nec conditions cubSobol_SI_g
Adding old examples and the beginning of the article

\usepackage{array,colortbl}
\usepackage{amsmath,amsfonts,amssymb,bm,listings} % no amsthm, Springer defines Theorem, Lemma, etc themselves
\usepackage{xspace}
\usepackage[autolinebreaks]{mcode}
\input FJHDef
\newcommand{\oerr}{e}

@@

Domains for integrals $N_j$ and $N_j^{\textup{tot}}$ can be rearranged to consider them as a single integral:
\begin{align*}
\mathbb{E}\left[ \Var \left(f(\underline{X})|X_j\right)\right] & = \int_{[0,1)^d}f(\underline{x})^2 d \underline{x} - \int_{[0,1)^{2d-1}}f(\underline{x})f(\underline{x}'_{-j},x_j)d \underline{x} d \underline{x}'_{-j} \\
& = \int_{[0,1)^{2d-1}}\left(f(\underline{x})^2-f(\underline{x})\right)f(\underline{x}'_{-j},x_j)d \underline{x} d \underline{x}'_{-j} \, . 
\end{align*}

\begin{align*}
\mathbb{E}\left[ \Var \left(f(\underline{X})|\underline{X}_{-j}\right)\right] & = \int_{[0,1)^d}f(\underline{x})^2 d \underline{x} - \int_{[0,1)^{d+1}}f(\underline{x})f(x'_{j},\underline{x}_{-j})d \underline{x} d {x}'_{j} \\
& = \int_{[0,1)^{d+1}}\left(f(\underline{x})^2-f(\underline{x})\right)f(x'_{j},\underline{x}_{-j})d \underline{x} d {x}'_{j} \, . 
\end{align*}

@@

>>>>

\usepackage{array,colortbl}
\usepackage{amsmath,amsfonts,amssymb,bm,listings} % no amsthm, Springer defines Theorem, Lemma, etc themselves
\usepackage{xspace}
\usepackage[autolinebreaks]{mcode}
\input FJHDef
\newcommand{\oerr}{e}
\newcommand{\verr}{\boldsymbol{\varepsilon}}
\newcommand{\tverr}{\tilde{\boldsymbol{\varepsilon}}}
\newcommand{\terr}{\tilde{\varepsilon}}
\newcommand{\vI}{\bvec{I}}
\newcommand{\tx}{\tilde{x}}

@@

Domains for integrals $N_j$ and $N_j^{\textup{tot}}$ can be rearranged to consider them as a single integral:
\begin{align*}
\mathbb{E}\left[ \Var \left(f(\underline{X})|X_j\right)\right] & = \int_{[0,1)^d}f(\underline{x})^2 d \underline{x} - \int_{[0,1)^{2d-1}}f(\underline{x})f(\underline{x}'_{-j},x_j)d \underline{x} d \underline{x}'_{-j} \\
& = \int_{[0,1)^{2d-1}}\left[f(\underline{x})^2-f(\underline{x})f(\underline{x}'_{-j},x_j)\right] d \underline{x} d \underline{x}'_{-j} \, . 
\end{align*}

\begin{align*}
\mathbb{E}\left[ \Var \left(f(\underline{X})|\underline{X}_{-j}\right)\right] & = \int_{[0,1)^d}f(\underline{x})^2 d \underline{x} - \int_{[0,1)^{d+1}}f(\underline{x})f(x'_{j},\underline{x}_{-j})d \underline{x} d {x}'_{j} \\
& = \int_{[0,1)^{d+1}}\left[f(\underline{x})^2-f(\underline{x})f(x'_{j},\underline{x}_{-j})\right] d \underline{x} d {x}'_{j} \, . 
\end{align*}

@@

\section{Improving Error Bounds for Stopping Criteria}
Consider the previous function ($\vx:=\vI$)
\[
f(\vx)=1-\frac{x_1}{x_2-x_3^2},\quad \vx\in[\tvx-\tverr,\tvx+\tverr].
\]
If our estimator is 
\[
\tf(\tvx)=\frac{1}{2}\left(f(\tx_1+\terr_1,\tx_2-\terr_2,\tx_3+\terr_3)+f(\tx_1-\terr_1,\tx_2+\terr_2,\tx_3-\terr_3)\right),
\]
we know that the error bound is clearly
\begin{align*}
\abs{f(\vx)-\tf(\tvx)}\leq\frac{1}{2} \abs{\frac{\tx_1+\terr_1}{\tx_2-\terr_2-\left(\tx_3+\terr_3\right)^2}-\frac{\tx_1-\terr_1}{\tx_2+\terr_2-\left(\tx_3-\terr_3\right)^2} }.
\end{align*}
If $\varepsilon_2=\varepsilon_3=0$, this error bound would directly be linear on $\varepsilon_1$. However, the difference in the denominators makes this error bound not clearly linearly convergent.

If we consider the Taylor expansion of our function with $\vx-\tvx=\verr$ (the difference is the real error $\verr\in[-\tverr,\tverr]$):
\begin{equation}
f(\vx)=f(\tvx)+\nabla f(\tvx)^t\verr+\frac{1}{2}\verr^t Hf(\tvx) \verr + \mathcal{O}(\norm{\verr}^3),
\end{equation}
we can take the following estimator,
\begin{align*}
\tf(\tvx)&=\frac{1}{2}\left(f(\tvx)+\nabla f(\tvx)^t\tverr+\frac{1}{2}\tverr^t Hf(\tvx) \tverr + f(\tvx)+\nabla f(\tvx)^t(-\tverr)+\frac{1}{2}(-\tverr)^t Hf(\tvx) (-\tverr) \right)\\
&=f(\tvx)+\frac{1}{2}\tverr^t Hf(\tvx) \tverr
\end{align*}
Thus, given that $Hf$ is symmetric, differentiable in the region of interest (denominator always positive), the error will be bounded by
\begin{align*}
\abs{f(\vx)-\tf(\tvx)}&=\abs{\nabla f(\tvx)^t\verr+\frac{1}{2}\left(\verr+\tverr\right)^t Hf(\tvx) \left(\verr-\tverr\right) + \mathcal{O}(\norm{\verr}^3)} \\
&\leq \max_{\vy\in[\tvx-\tverr,\tvx+\tverr], \vz\in[-\tverr,\tverr]}\abs{\nabla f(\tvx)^t\vz+\frac{1}{2}(\vz+\tverr)^t Hf(\vy)(\vz-\tverr)}
\end{align*}

Clearly, because of signs the maximum $\vz$ is for $\vz=\{-\tilde{\varepsilon_1},\tilde{\varepsilon_2},-\tilde{\varepsilon_3}\}$.
